---
title: "Health Care Fraud EDA"
output: html_notebook
---

```{r}
library(tidyverse)

docs = read_csv('../data/combinedData.csv');
target = read_csv('../data/combinedTarget.csv');

data = docs %>% 
  left_join(target, by=c('Provider','Set')) %>% 
  select(-c('X1.x','X1.y'));
```
netAnal takes in the data, state number, and counties and produces a bipartites network
graph of either the

- Provider-Patient Network (type = 'propat')
- Provider-Doctor Network (type = 'prodoc')
- Patient-Doctor Network (type = 'patdoc')

User can also specify the way to layout the diagram. Usually 'stress' is the best layout to visualize these networks. For a more hierarchical layout try 'sugiyama'.

User can also look at all counties within a given state by setting county = 'all'.
Though for large states or patdoc networks this is not recommended since it takes a long time to plot and graphs are not that informative. 

```{r}
source("analNet.R")
state = 'Oklahoma'
county = c(100,200)
netAnal(data, state, county, type='propat', layout = 'stress')
netAnal(data, state, county, type='prodoc', layout = 'kk')
netAnal(data, state, county, type='patdoc', layout = 'stress')
```

```{r}
source("getNet.R")
source("plotNet.R")


bnet = propat(data, c('Oklahoma'), 100)

#plotProDoc(bnet, layout = 'stress')

plot(log(degree.distribution(bnet)),
     type="b",xlab="Degree",ylab="Proportion")

#ggsave(filename=paste0('../visualizations/networks/texas100_patdoc_stress.png'),plot=last_plot())
op <- par(mfrow=c(1,2)) 
plot(degree.distribution(bnet),xlab="Degree", ylab="Proportion") 
plot(degree.distribution(g), xlab="Degree",ylab="Proportion") 
par(op)
```

```{r}

# mean_path_length = function(net){
#   paths = data.frame(distances(net, v=V(net), 
#                                to = V(net)))
#   isolated = which(degree(net)==0)
#   if (length(isolated)==0){
#     paths_mean = rowSums(paths)/length(paths)
#   } else {
#     paths_rowdel = paths[-isolated,]
#     paths_coldel = paths_rowdel[,-isolated]
#     paths_mean = rowSums(paths_coldel)/length(paths_coldel)
#   }
#   return(paths_mean)
# 
# }

deglist = list()
annlist = list()
btwnlist = list()
eigenlist = list()

for (state in data$State %>% unique()) {
    # Get Provider-Patient Network for all counties in the state
    bnet = propat(data, state, 'all')
    # Project bipartite network into two one mode networks
    bn.pr <- bipartite.projection(bnet)
    # Get Provider network - affiliated through shared patients
    bn.provider <- bn.pr$proj2
    
    # Calculate Degrees
    deg = degree(bn.provider)
    deg = tibble(names(deg), deg)
    colnames(deg) = c('Provider','Degree')
    
    # Calculate Betweeenness
    btwn = betweenness(bn.provider)
    btwn = tibble(names(btwn), btwn)
    colnames(btwn) = c('Provider','Betweenness')
    
    # Calculate Values of the First Eigenvector of the Graph Matrix
    eign = eigen_centrality(bn.provider)
    eign = tibble(names(eign), eign)
    colnames(eign) = c('Provider','Eigenvector')
    
    # Calculate Average Nearest Neighbors
    ann = knn(bn.provider)
    ann = ann$knn
    ann = tibble(names(ann), ann)
    colnames(ann) = c('Provider','Avg.NN')
    
    # Add to list by state
    deglist[[state]] = deg
    btwnlist[[state]] = btwn 
    eigenlist[[state]] = eign 
    annlist[[state]] = ann 
}

propatDeg <- dplyr::bind_rows(deglist)
propatBtwn <- dplyr::bind_rows(btwnlist)
propatEign <- dplyr::bind_rows(eignlist)
propatANN <- dplyr::bind_rows(annlist)

#############################################################################

deglist = list()
annlist = list()
btwnlist = list()
eigenlist = list()

for (state in data$State %>% unique()) {
    # Get Provider-Doctor Network for all counties in the state
    bnet = prodoc(data, state, 'all')
    # Project bipartite network into two one mode networks
    bn.pr <- bipartite.projection(bnet)
    # Get Provider network - affiliated through shared doctors
    bn.provider <- bn.pr$proj2
    
    # Calculate Degrees
    deg = degree(bn.provider)
    deg = tibble(names(deg), deg)
    colnames(deg) = c('Provider','Degree')
    
    # Calculate Betweeenness
    btwn = betweenness(bn.provider)
    btwn = tibble(names(btwn), btwn)
    colnames(btwn) = c('Provider','Betweenness')
    
    # Calculate Values of the First Eigenvector of the Graph Matrix
    eign = eigen_centrality(bn.provider)
    eign = tibble(names(eign), eign)
    colnames(eign) = c('Provider','Eigenvector')
    
    # Calculate Average Nearest Neighbors
    ann = knn(bn.provider)
    ann = ann$knn
    ann = tibble(names(ann), ann)
    colnames(ann) = c('Provider','Avg.NN')
    
    # Add to list by state
    deglist[[state]] = deg
    btwnlist[[state]] = btwn 
    eigenlist[[state]] = eign 
    annlist[[state]] = ann 
}
#############################################################################

prodocDeg <- dplyr::bind_rows(deglist)
prodocBtwn <- dplyr::bind_rows(btwnlist)
prodocEign <- dplyr::bind_rows(eignlist)
prodocANN <- dplyr::bind_rows(annlist)

```

```{r}

propatDeg_clean = propatDeg %>% group_by(Provider) %>% summarise(patDegMax = max(Degree, na.rm=TRUE))
propatBtwn_clean = propatBtwn %>% group_by(Provider) %>% summarise(patBtwnMean = mean(Betweenness, na.rm=TRUE))
propatEign_clean = propatEign %>% group_by(Provider) %>% summarise(patEignMean = mean(Eigenvector, na.rm=TRUE))
propatANN_clean = propatANN %>% group_by(Provider) %>% summarise(patMANN = mean(Avg.NN, na.rm=TRUE))

prodocDeg_clean = prodocDeg %>% group_by(Provider) %>% summarise(docDegMax = max(Degree, na.rm=TRUE))
prodocBtwn_clean = prodocBtwn %>% group_by(Provider) %>% summarise(docBtwnMean = mean(Betweenness, na.rm=TRUE))
prodocEign_clean = prodocEign %>% group_by(Provider) %>% summarise(docEignMean = mean(Eigenvector, na.rm=TRUE))
prodocANN_clean = prodocANN %>% group_by(Provider) %>% summarise(docMANN = mean(Avg.NN, na.rm=TRUE))



propatNet = propatDeg_clean %>% 
  left_join(propatBtwn_clean, by='Provider') %>% 
  left_join(propatEign_clean, by='Provider') %>% 
  left_join(propatANN_clean, by='Provider')

prodocNet = prodocDeg_clean %>% 
  left_join(prodocBtwn_clean, by='Provider') %>% 
  left_join(prodocEign_clean, by='Provider') %>% 
  left_join(prodocANN_clean, by='Provider')

write_csv(prodocNet,'../../prodocNet.csv')
write_csv(propatNet,'../../propatNet.csv')

```

```{r}
bnet = prodoc(data, c('California'), 'all')
bn.pr = bipartite.projection(bnet)
bn.provider <- bn.pr$proj2

deg = degree(bn.provider)
str = strength(bn.provider)
ann = knn(bn.provider)
ann = ann$knn

deg = tibble(names(deg), deg)
str = tibble(names(str), str)
ann = tibble(names(ann), ann)

colnames(deg) = c('Provider','Degree')
colnames(str) = c('Provider','Strength')
colnames(ann) = c('Provider','Avg.NN')

deg %>% left_join(ann, by = 'Provider')

```
```{r}
# wc = cluster_fast_greedy(bnet)
# modularity(wc)
# membership(wc)
# 
# #plot(distance_table(bn.provider, directed = FALSE))
# mean_distance(bn.provider)

# By default weighted by graph edge weights unless passed
# Algo is chosen to take into account edge weights
bnet = propat(data, c('Oklahoma'), 'all')
bn.pr = bipartite.projection(bnet)
bn.provider <- bn.pr$proj2

paths = data.frame(distances(bn.provider, v=V(bn.provider), to = V(bn.provider)))
isolated = which(degree(bn.provider)==0)
paths_rowdel = paths[-isolated[[1]],]
paths_coldel = paths_rowdel[,-isolated[[1]]]
paths_mean = rowSums(paths_coldel)/(length(paths_coldel)-1)
paths_mean

```

```{r}
bnet = prodoc(data, c('Hawaii'), 'all')
bn.pr = bipartite.projection(bnet)
bn.provider <- bn.pr$proj2
g = connect(bn.provider,2)

ggraph(bn.provider, layout='kk')+
    geom_edge_link0(alpha=0.5, edge_colour = "grey66") + 
    geom_node_point(aes(color = fraud, size = size)) +
    #geom_node_point() +
    scale_size_continuous(range = c(1,5), guide=FALSE)+
    theme_graph() +
    theme(legend.position = "bottom")


ggraph(g, layout='kk')+
    geom_edge_link0(alpha=0.5, edge_colour = "grey66") + 
    geom_node_point(aes(color = fraud, size = size)) +
    #geom_node_point() +
    #scale_size_continuous(range = c(1,5), guide=FALSE)+
    theme_graph() +
    theme(legend.position = "bottom")

```
```{r}
vignette('ergm-term-crossRef')
```
```{r}
crnd <- runif(500,1,8)
cmp_prp <- sapply(crnd,function(x)
max(clusters(erdos.renyi.game(n=1000, p=x/999))$csize)/1000)

smoothingSpline <- smooth.spline(crnd,cmp_prp, spar=0.25)
plot(crnd,cmp_prp,col='grey60', xlab="Avg. Degree",
ylab="Largest Component Proportion") 
lines(smoothingSpline,lwd=1.5)
```
```{r}
library(lattice)

n_vect <- rep(c(50,100,500,1000,5000),each=50) 
g_diam <- sapply(n_vect,function(x) diameter(erdos.renyi.game(n=x,p=6/(x-1))))
bwplot(g_diam ~ factor(n_vect), panel = panel.violin,
    xlab = "Network Size", ylab = "Diameter")
```


```{r}
ggraph(bnet, layout ='stress')+
    geom_edge_link0(alpha=0.5, edge_colour = "grey66", aes(width = weights)) + 
    #geom_node_point(aes(color = fraud, size = size), shape = V(bnet)$shape) +
    geom_node_point(aes(
      #fitler = size >= 10,
      color = fraud,
      size = size), shape = V(bnet)$shape) +
    geom_node_text(aes(filter = size >= 50, label = name, size=3),family="serif", repel=TRUE)+
    scale_color_brewer(palette = "Dark2")+
    scale_edge_width_continuous(range = c(0.2,3), guide=FALSE)+
    scale_fill_manual(values = palette) +
    scale_size_continuous(range = c(1,5), guide=FALSE)+
    theme_graph() +
    theme(legend.position = "bottom")
  
    #ggsave(filename=paste0('./visualizations/networks/pb_5_200_sugiyama.png'),plot=last_plot())
}
```

```{r}




```





```{r}
bn.pr <- bipartite.projection(bnet)
bn.patient <- bn.pr$proj1 
bn.provider <- bn.pr$proj2 
graph.density(bn.patient)
#get.adjacency(bn.patient,sparse=FALSE,attr="weight")
```
```{r}
shapes <- c("circle","square") 
colors <- c("blue","red")
op <- par(mfrow=c(1,2)) 
# plot(bn.patient,vertex.color="blue",
#      vertex.shape="circle",main="Patients", 
#      edge.width=E(bn.patient)$weight*2, 
#      vertex.size=15,vertex.label.degree=-pi/2, 
#      vertex.label.dist=1.2,vertex.label.cex=1)
# plot(bn.provider,vertex.color="red", 
#      vertex.shape="square",main="Providers", 
#      edge.width=E(bn.patient)$weight*2, 
#      vertex.size=15,vertex.label.degree=-pi/2, 
#      vertex.label.dist=1.2,vertex.label.cex=1)


ggraph(bn.patient, layout='stress') +
  geom_edge_link0(color="gray50", width=0.8, alpha=0.5) +  
  geom_node_point() +
  geom_node_text(aes(filter = size >= 10, label = name, size=3),family="serif", repel=TRUE)+
  theme_graph() +
  theme(legend.position = "bottom")


ggraph(bn.provider, layout='stress') +
  geom_edge_link0(color="gray50", width=0.8, alpha=0.5) +
  geom_node_text(aes(filter = size >= 10, label = name, size=3),family="serif", repel=TRUE)+
  geom_node_point(aes(color = fraud, size = size)) +
  scale_size_continuous(range = c(1,5), guide=FALSE)+
  theme_graph() +
  theme(legend.position = "bottom")
par(op)
```

```{r}



df.prom <- data.frame(
  btw = betweenness(bn.provider), 
  evc = evcent(bn.provider),
  inf = infocent(bn.provider), 
  flb = flowbet(bn.provider)
)
```


```{r}
h2 <- subgraph.edges(h1, 
                     E(h1)[inc(V(h1)[name %in% c("The Wolf of Wall Street", 
                                                     "Gangs of New York",
                                                     "The Departed")])]) 
plot(h2, layout = layout_with_kk)
```
```{r}


print('Degree Distribution of Patients')
print(table(degree(binet,v=V(binet)[type==FALSE])))

print('Degree Distribution of Providers')
print(table(degree(binet,v=V(binet)[type==TRUE])))

print('Mean Degree of Patients')
print(mean(degree(binet,v=V(binet)[type==FALSE])))

print('Mean Degree of Providers')
print(mean(degree(binet,v=V(binet)[type==TRUE])))
```
```{r}
V(binet)$deg = degree(binet)
V(binet)[type==FALSE & deg > 4]$name
```

```{r}
busy_patients <- data.frame(cbind(Patient = V(binet)[type==FALSE & deg > 4]$name, 
                               Provider = V(binet)[type==FALSE & deg > 4]$deg
))
busy_patients
```
```{r}
beneP %>% 
  select(Provider,BeneID) %>% 
  group_by(BeneID) %>% 
  tally() %>% 
  filter(n > 4) %>% 
  arrange(desc(n))

bene = beneP %>% 
  select(Provider,BeneID) %>% 
  group_by(BeneID) %>% 
  tally()
mean(bene$n)
```


## Great example of how a new metric can be created... though maybe this can also be done easliy with dataframe groupings.. 
```{r}
for (i in 161:1365) {
  V(h1)[i]$totrating <- sum(V(h1)[nei(i)]$IMDBrating)
}

pop_actor <- data.frame(cbind(Actor = V(h1)[type==FALSE & totrating > 40]$name, 
                              Popularity = V(h1)[type==FALSE & totrating > 40]$totrating)) 

pop_actor[order(pop_actor$Popularity,decreasing=TRUE),]

scatter.smooth(num,avgpop,col="lightblue", 
               ylim=c(2,10),span=.8, xlab="Number of Movies", ylab="Avg. Popularity")
```


```{r}
h1.pr <- bipartite.projection(h1) 
h1.act <- h1.pr$proj1
h1.mov <- h1.pr$proj2
h1.act
```

```{r}
op <- par(mar = rep(0, 4)) 
plot(bn.provider,vertex.color="red", 
     vertex.shape="circle", 
     vertex.size=(E(bn.provider)$weight+1)/2, 
     vertex.label=NA)

par(op)
no.clusters(bn.provider)

```

```{r}
bn.provider <- induced.subgraph(bn.provider, vids=clusters(bn.provider)$membership==1)
plot(bn.provider,vertex.color="red", 
     edge.width=sqrt(E(bn.provider)$weight), 
     vertex.shape="circle", 
     vertex.size=E(bn.provider)$weight, 
     vertex.label=NA)

```


```{r}
h1.pr <- bipartite.projection(binet) 
h1.act <- h1.pr$proj1
h1.mov <- h1.pr$proj2
h1.act
```






```{r}
per_route = data_pdc_5 %>%
  group_by(Doctor) %>%
  summarise(weight = sum(n)) %>%
  arrange(desc(weight)) %>%
  ungroup() %>%
  rowid_to_column()
per_route
```

```{r}

#by(data_pdc_5, data_pdc_5$Provider, function(x) t(combn(as.vector(x$Doctor), 2)))
adjacency_mat = data_pdc_5 %>%
  select(Provider, Doctor, n) %>% 
  spread(Doctor, n, fill=0) %>% 
  tibble::column_to_rownames("Provider")


# edges = per_route %>%
#   left_join(nodes, by=c('Doc1' = 'label')) %>%
#   rename(from=id)
# 
# edges = edges %>% 
#   left_join(nodes, by = c("Doc2" = 'label')) %>% 
#   rename(to = id)
# 
# edges = select(edges,from, to, weight)
# 
# 
# docNet <- network(edges, vertex.attr = nodes, 
#                           matrix.type = "edgelist", ignore.eval = FALSE)
```

```{r}
adjacency_mat %>% head() %>% sum()
```
```{r}
net1 <- network(adjacency_mat,matrix.type="adjacency") 
```

```{r}
library(igraph)
adjm1<-matrix(sample(0:1,1000,replace=TRUE,prob=c(0.9,01)),nc=10) 
g1<-graph.adjacency(adjm1)
x11()
plot(g1)
```

```{r}
generate_Network = function(docs){
  source = docs %>% 
    distinct(Doc1) %>% 
    rename(label = Doc1) %>% mutate(type = "Attending")
  
  destination = docs %>% 
    distinct(Doc2,Connection) %>% 
    mutate(type = ifelse(Connection=='OperatingPhysician','Operating','Other')) %>% 
    rename(label = Doc2) %>% 
    select(label,type)
  
  nodes = full_join(source,destination, by=c('label','type')) %>% rowid_to_column("id") %>% drop_na()
  
  per_route = docs %>% 
    group_by(Doc1,Doc2) %>% 
    summarise(weight = sum(ClaimsFiled)) %>% 
    ungroup() %>% rowid_to_column()
  
  edges = per_route %>% 
    left_join(nodes, by=c('Doc1' = 'label')) %>% 
    rename(from=id)
  
  edges = edges %>% 
    left_join(nodes, by = c("Doc2" = 'label')) %>% 
    rename(to = id)
  
  edges = select(edges,from, to, weight)

  
  docNet <- network(edges, vertex.attr = nodes, 
                            matrix.type = "edgelist", ignore.eval = FALSE)

}
```

```{r}
data = filter(docs, State == 23)# %>% select(-X1)
data = data[complete.cases(data),]
generate_Network(data)
```

```{r}
edges
```

```{r}
library('network')

doc_net <- network(edges,  vertex.attr=nodes, matrix.type="edgelist", 
                loops=F, multiple=F, ignore.eval = F)

#detach('package:network')
library(ggraph)
library(igraph)

ggraph(doc_net) +
  geom_edge_fan(color="gray50", width=0.8, alpha=0.5) + 
  geom_node_point() +
  theme_bw() # add nodes to the plot

```
```{r}
ggraph(doc_net) +
  geom_edge_arc(color="gray", curvature=0.3, aes(size=weight)) +            
  geom_node_point(color="orange") +     
  geom_node_text(aes(label = label), size=2, color="black", repel=T) +
  theme_void()
```

```{r}
par(mar=c(0,0,0,0))

render.d3movie(doc_net, usearrows = F, displaylabels = F, bg="#111111", 
       vertex.border="#ffffff", 
       #vertex.col =  net3 %v% "col",
       #vertex.cex = (net3 %v% "audience.size")/8, 
       edge.lwd = (net3 %e% "weight")/3, 
       edge.col = '#55555599',
       vertex.tooltip = paste("<b>Name:</b>", (net3 %v% 'label')), 
                              #"<br>",
                              #"<b>Type:</b>", (net3 %v% 'type.label')),
       edge.tooltip = paste("<b>Connection to Source:</b>", (net3 %e% 'Connection'), "<br>", 
                            "<b>Number of Claims Filed:</b>", (net3 %e% "weight" ) ),
       launchBrowser=F, filename="Doc-Network.html")
```



```{r}
save(nodes, file = "nodes.RData")
save(edges, file = "edges.RData")
```


```{r}
library(network)

routes_network <- network(edges, vertex.attr = nodes, 
                          matrix.type = "edgelist", ignore.eval = FALSE)
```
```{r}
plot(routes_network, vertex.cex = 3)
plot(routes_network, vertex.cex = 3, mode = "circle")

```
```{r}
detach(package:network)
rm(routes_network)
library(igraph)
```

```{r}
routes_igraph <- graph_from_data_frame(d = edges, vertices = nodes, directed = TRUE)
```
```{r}
plot(routes_igraph, edge.arrow.size = 0.2)
plot(routes_igraph, layout = layout_with_graphopt, edge.arrow.size = 0.2)
```

```{r}
library(tidygraph)
library(ggraph)
```
```{r}
routes_tidy <- tbl_graph(nodes = nodes, edges = edges, directed = TRUE)
```

```{r}
routes_tidy
```

```{r}
routes_tidy %>% 
  activate(edges) %>% 
  arrange(desc(weight))
```
```{r}
ggraph(routes_tidy, layout = 'graphopt') + 
  geom_node_point() + 
  geom_edge_link(aes(width=weight), alpha=0.8) +
  scale_edge_width(range=c(0.1,2)) +
  geom_node_text(aes(label=label), repel=TRUE) +
  labs(edge_width = "Letters") +
  theme_graph()

ggraph(routes_igraph, layout = "linear") + 
  geom_edge_arc(aes(width = weight), alpha = 0.8) + 
  scale_edge_width(range = c(0.2, 2)) +
  geom_node_text(aes(label = label)) +
  labs(edge_width = "Letters") +
  theme_graph()

```
```{r}
library(visNetwork)
library(networkD3)

visNetwork(nodes,edges)
```

```{r}
edges = mutate(edges, width = weight/5 + 1)

visNetwork(nodes,edges) %>% 
  visIgraphLayout(layout = "layout_with_fr") %>% 
  visEdges(arrows="middle")
```

```{r}
nodes_d3 <- mutate(nodes, id = id - 1)
edges_d3 <- mutate(edges, from = from - 1, to = to - 1)
```

```{r}
forceNetwork(Links = edges_d3, Nodes = nodes_d3, Source = "from", Target = "to", 
             NodeID = "label", Group = "id", Value = "weight", 
             opacity = 1, fontSize = 16, zoom = TRUE)
```
```{r}
sankeyNetwork(Links = edges_d3, Nodes = nodes_d3, Source = "from", Target = "to", 
              NodeID = "label", Value = "weight", fontSize = 16, unit = "Letter(s)")
```
```{r}
netmat1 <- rbind(c(0,1,1,0,0), c(0,0,1,1,0), c(0,1,0,0,0), c(0,0,0,0,0), c(0,0,1,0,0))
rownames(netmat1) <- c("A","B","C","D","E") 
colnames(netmat1) <- c("A","B","C","D","E")
net1 <- network(netmat1,matrix.type="adjacency") 
class(net1)
```

```{r}
gplot(net1, vertex.col=2, displaylabels=TRUE)
```

```{r}
data = read_csv('./data/combinedData.csv')
#target = read_csv('./data/combinedTarget.csv')
```

```{r}
library(Hmisc)
library(psych)
data_summary = data %>% select_if(is.numeric) %>% psych::describe()
```

```{r}
data_summary %>% mutate(n = abs(n-693603))
```
```{r}
library(statnet)
as.matrix(net1, matrix.type='edgelist')
```

```{r}
set.vertex.attribute(net1, "gender", c("F","F","M","F","M"))
net1 %v% "alldeg" = degree(net1)
list.vertex.attributes(net1)

get.vertex.attribute(net1, "alldeg")

set.edge.attribute(net1, "rndval", runif(network.size(net1),0,1))

netval1 <- rbind(c(0,2,3,0,0), c(0,0,3,1,0), c(0,1,0,0,0), c(0,0,0,0,0), c(0,0,2,0,0))
netval1 <- network(netval1,matrix.type="adjacency", ignore.eval=FALSE,names.eval="like")
```

